---
title: "Regression models. Week 4. Course project"
author: "Grigory Sharkov"
date: "23 mars 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

```

## Summary
The goal of this project is to analyse mtcars dataset to study correlation between the fuel consumtion of cars using manual and automatic transmition.

## Exploratory data analysis  
First, lets load and check the available data:  
```{r observation}
library(datasets)
data("mtcars")
head(mtcars)

ggplot(mtcars,aes(x=factor(am),y=mpg)) + 
  geom_boxplot() +
  ggtitle("Average fuel consomation depending on transmission type") +
  scale_x_discrete(labels=c("1"="Manual","0"="Auto"))
```  

## Regression analysis  
  In general we can see that average consumption is higher for cars automatic transmission rather than for cars with manual transmission. It can be confirmed by a regression model:  
```{r reg1}
fit <- lm(mpg~am, data=mtcars)
summary(fit)
```  
R-squared = 0.3598 tells us that only 35% of the decrease comes from the fact of changing the transmission type and there are other factors that influence 65% of the change.